A community-maintained standard library of population genetic models

### 2019-12-20 popSimManu.tex
Typos and minor formatting.

Given the genome data and simulation model descriptions defined within the
library, it is then straightforward to run accurate, standardized simulations
across a range of organisms. \Stdpopsim has a Python API and a user-friendly
command line interface, allowing users with minimal experience direct access to
state-of-the-art simulations. Simulations are output in the ``tree sequence''
format \citep{kelleher2016efficient,kelleher2018efficient,kelleher2019inferring}, which
contains complete genealogical information about the simulated samples, is
extremely compact, and can be processed efficiently using the \tskit library
\citep{kelleher2016efficient,kelleher2018efficient}. Currently,
\stdpopsim uses the  \texttt{msprime} coalescent simulator \citep{kelleher2016efficient}
as the default simulation engine. We plan to include other simulation
engines to support scenarios that cannot be modelled under the coalescent framework,
and have already implemented \texttt{SLiM} \citep{haller2019tree,haller2019slim} as
an additional backend.

@@

% JK here --- I think it would really help if we described what the models
% were, briefly, rather than saying who inferred them.
In Figure \ref{fig:n_t_ragsdale} we present results from our $N(t)$ analysis pipeline
run on whole genome simulations under under a sophisticated demographic model
and empirical genetic map and a model of human migration out of Africa
that includes archaic admiture \citep{ragsdale2019models}. In each column of this figure
we show inferred $N(t)$ for the three extant populations in the model.
In each row we show comparisons among the methods (note that we compare two differing
sample sizes for \MSMC).
There is no single ``true'' reference for effective population size
because of model misspecification -- the inference methods are fitting a single population model
to data simulated from mulitple populations.
However, many methods work by matching coalescence time distributions,
and a single-population model with varying population size can match any coalescence time distribution
(in which case coalescence rate is the inverse of the effective size).
For this reason, solid black lines do not show historical census sizes,
but rather inverse coalescence rates calculated analytically in \texttt{msprime} (see Appendix).
Blue lines show estimates from each of three replicate whole genome simulations.
While there is variation in accuracy among methods, populations, and individual replicates,
generally the methods are accurate for this model of human history.

>>>>

Given the genome data and simulation model descriptions defined within the
library, it is then straightforward to run accurate, standardized simulations
across a range of organisms. \Stdpopsim has a Python API and a user-friendly
command line interface, allowing users with minimal experience direct access to
state-of-the-art simulations. Simulations are output in the ``tree sequence''
format \citep{kelleher2016efficient,kelleher2018efficient,kelleher2019inferring}, which
contains complete genealogical information about the simulated samples, is
extremely compact, and can be processed efficiently using the \tskit library
\citep{kelleher2016efficient,kelleher2018efficient}. Currently,
\stdpopsim uses the  \texttt{msprime} coalescent simulator \citep{kelleher2016efficient}
as the default simulation engine. We plan to include other simulation
engines to support scenarios that cannot be modeled under the coalescent framework,
and have already implemented \texttt{SLiM} \citep{haller2019tree,haller2019slim} as
an additional backend.

@@

% JK here --- I think it would really help if we described what the models
% were, briefly, rather than saying who inferred them.
In Figure \ref{fig:n_t_ragsdale} we present results from our $N(t)$ analysis pipeline
run on whole genome simulations under under a sophisticated demographic model
and empirical genetic map and a model of human migration out of Africa
that includes archaic admixture \citep{ragsdale2019models}. In each column of this figure
we show inferred $N(t)$ for the three extant populations in the model.
In each row we show comparisons among the methods (note that we compare two differing
sample sizes for \MSMC).
There is no single ``true'' reference for effective population size
because of model misspecification---the inference methods are fitting a single population model
to data simulated from mulitple populations.
However, many methods work by matching coalescence time distributions,
and a single-population model with varying population size can match any coalescence time distribution
(in which case coalescence rate is the inverse of the effective size).
For this reason, solid black lines do not show historical census sizes,
but rather inverse coalescence rates calculated analytically in \texttt{msprime} (see Appendix).
Blue lines show estimates from each of three replicate whole genome simulations.
While there is variation in accuracy among methods, populations, and individual replicates,
generally the methods are accurate for this model of human history.
